The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-10-07 razzo-results.tex
Move figures and their TeX files to the same folder as the other TeX, as using a subfolder does not scale (that is, renders the TeX unusable to be used in a thesis)
Do not '\input' in a file added by '\input', as it scales badly (that is, it renders the TeX unusable for a thesis)
Depend on master branch

\section{Results}
Here we present the results as show in Fig.~\ref{fig:results}...

\input{razzo-figures/fig_results.tex}

>>>>

\section{Results}

The inference error made for each of the parameter combinations
is shown in Figures ~\ref{fig:errors_yule} and ~\ref{fig:errors_bd}. 
For both extinction rates,
we find that the error increases as $\nu$
and $q$ increase. 
Also in line with RJCB's predictions, 
we find no difference between the two extinction rates.
